---
title: "First test with graph.cpt package"
subtitle: "Case of change in a sequence of SPD matrices"
author: "Vincent Runge"
date: "09/05/2024"
output:
  html_document:
    keep_md: true
    css: styles.css
    toc: true
    toc_float: true
    highlight: tango
    number_sections: true
---


```{r setup, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

```{r, message=FALSE}
library(graph.cpt) #our package
```

The outline of this document is as follows. In a first example, we test our functions on a simple case. 

- We generate data (time series) with a given SPD structure, with a few changes

- We define the graph structure used to generate the data (as if we knew the state values, oracle case)

- We use the `graph_cpt_manifold` function to infer the initial change point structure

- We discuss the result

In a second example, we also search a way to infer good state values for the graph. 

# A simple example

We test the `dust_R_1D` function with different pruning options and different data models.

```{r}
data <- dataGenerator_SPD(chpts = 10, d = 3, eigenvalues_mat = matrix(c(1,2,3),3,1))
data
```

